Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-07-29 main.Rmd
global threshold code update

  harmonies <- sm %>%
  harmony(ugran = "month",
          filter_in = "wknd_wday", 
          filter_out = c("hhour", "fortnight"))

global_harmony <- sm %>%
  global_threshold(harmony_tbl = harmonies,
                   response = "general_supply_kwh")%>%
  # select(facet_variable,x_variable,
  #        facet_levels,x_levels,MMPD) %>% 
  rename(`facet variable` = facet_variable,
         `x-axis variable` = x_variable,
         `facet levels` = facet_levels,
         `x-axis levels` = x_levels,
         `average maximum variation` = MMPD)

@@

  knitr::kable(smart_harmony,
               format = "latex",
               booktabs = TRUE,
                caption = "Harmonies with two cyclic granularity one placed on facet and the other on x-axis along with their number of categories/levels. Out of 42 possible combinations of cyclic granularities, only these 10 are harmony pairs. The harmony pairs are ranked basis highest to lowest MMPD, only the first 6 of which are significant.") %>%
    #row_spec(0, bold = TRUE) %>%
    kable_styling()
```

>>>>

  harmonies <- sm %>%
  harmony(ugran = "month",
          filter_in = "wknd_wday", 
          filter_out = c("hhour", "fortnight"))
set.seed(12345)
global_harmony <- sm %>%
  global_threshold(harmony_tbl = harmonies,
                   response = "general_supply_kwh", nsamp = 5)%>%
  select(facet_variable,x_variable,
         facet_levels,x_levels,MMPD, gt_MMPD) %>%
  rename(`facet variable` = facet_variable,
         `x-axis variable` = x_variable,
         `facet levels` = facet_levels,
         `x-axis levels` = x_levels,
         `above threshold` = gt_MMPD)

@@

  knitr::kable(global_harmony,
               format = "latex",
               booktabs = TRUE,
                caption = "Harmonies with two cyclic granularity one placed on facet and the other on x-axis along with their number of categories/levels. Out of 42 possible combinations of cyclic granularities, only these 10 are harmony pairs. The harmony pairs are ranked basis highest to lowest MMPD, only the first 6 of which are significant.") %>%
    #row_spec(0, bold = TRUE) %>%
    kable_styling()
```
